\chapter{Introduction} \label{sec:introduction}

Imagine you are lost in a jungle, wandering alone in an unfamiliar environment fraught with danger and uncertainty. Your survival depends on your ability to learn to differentiate between the things you can eat and the things that can eat you. This is an expensive and risky process given the need for movement and trial and error. One day you come across another individual that is more familiar with your surroundings. Together you develop a common sign language (symbols) that you can use to know more about the threats and opportunities in this hostile environment. Along with real examples, these symbols allow you to overcome your struggle in the jungle.

Learning in humans involves being introduced to many examples. The more examples the learner is exposed to the more effective the learning process is. This however is not always possible given the cost (energy and time) and risk (injury and death) involved. The ability of a single learner to learn effectively is therefore hampered by the lack of a sufficient number of examples. However, societies evolved to overcome this challenge by developing mechanisms by which accumulated knowledge is shared amongst individuals in the group\cite{DBLP:journals/corr/abs-1203-2990}.

Similar to how the lack of a sufficient number of examples can make learning difficult for humans, machine learning models also experience difficulty in finding a suitable representation when they are trained with a limited dataset. The research presented in this thesis draws analogies between training neural network models and learning in humans.  We investigate how the presence of symbols while training artificial neural networks with impoverished datasets can improve the effectiveness of these models, just like the exchange of symbols between individual human learners can help them overcome their learning challenges.

We begin this chapter by providing a brief introduction to machine learning and specifically deep learning followed by an overview of learning with symbols. We then discuss our research scope and objective. Finally, we present an outline to the remainder of the thesis.

\input{introduction/introduction-to-machine-learning/introduction-to-machine-learning}

\input{introduction/learning-with-symbols/learning-with-symbols}

\input{introduction/research-objective-scope/research-objective-scope}

\input{introduction/thesis-outline/thesis-outline}