\chapter{Conclusion} \label{sec:findings-and-conclusion}

In Chapter 1 we described the challenges that an individual human would have in learning to survive alone in the jungle. She or he would have to observe a large number of examples of a concept in order to learn the concept. We discussed how by using shared knowledge from other humans and relying on their past experiences, the lone learner is able to overcome learning from impoverished datasets. In traditional machine learning, computer systems do not have the benefit of shared knowledge and past experiences. They must rely on sufficient numbers of training examples to achieve the same level of accuracy as a human would.

In Chapter 3 we hypothesized that in the same manner that human learners are able to use shared knowledge to overcome the challenges they encounter while learning, machine learning systems can overcome impoverished datasets using shared knowledge. Our theory states that by introducing a clear and concise symbol channel, that is analogous to the knowledge shared by human learners, neural networks can overcome learning difficulties caused by small training sets and produce more accurate models. In Chapter 4, we presented a series of experiments that show how this theory can be applied to training recurrent neural networks to perform basic arithmetic on images of handwritten digits.

This final chapter starts by providing a summary of our findings and reflects on the objectives of our research (Section \ref{sec:findings-and-conclusion-summary-of-findings}). Next we describe the contributions made by our work (Section \ref{sec:findings-and-conclusion-research-contributions}). Finally, a list of suggested future work is presented in Section \ref{sec:findings-and-conclusion-future-work}.

\input{findings-and-conclusion/summary-of-findings/summary-of-findings}

\input{findings-and-conclusion/research-contributions/research-contributions}

\input{findings-and-conclusion/future-work/future-work}