\section{Temperature Encoding Experiments} \label{sec:empirical-studies-temperature-encoding-experiments}

So far we were able to show that symbols improve the effectiveness of the learning process when training neural networks on limited datasets. We have however failed to show that they can generalize to digit combinations that they have not seen before. In Section \ref{sec:theory-approach-methodology-temperature-encoding} we described an alternative representation for our symbols, namely the temperature encoded symbols. We explained our expectation that temperature encodings will improve the ability of the networks to generalize to unseen combinations since they are able to encapsulate three characteristics that are important in developing an algorithm that performs arithmetic. Specifically, these characteristics are, (1) the ability of the symbols to represent the ordinal relationship between digits, (2) the ability to represent the quantity of the digits and (3) the ability to capture the function of the operator. The prior experiment showed that one-hot vectors are capable of capturing the function of the operator, as shown by the ability of the models to internally represent the carry forward behavior of addition. They however fail in providing the other two properties. This final set of experiments investigates the ability of temperature encoded symbols to capture all three characteristics and presents a solution to our problem. 

\input{empirical-studies/temperature-encoding-experiments/experiment-6/experiment-6}

\input{empirical-studies/temperature-encoding-experiments/experiment-7/experiment-7}